% greeting card document using gcard package, showing basic techniques of size 
% selection and horizontal and vertical placement of text

% For landscape orientation, include ``landscape'' as a global
% option, and call the geometry package explicitly to specify your
% output driver.  This example assumes dvips.  (The explicit \usepackage{geometry}
% is unnecessary with pdftex, and in fact pdftex will even ignore other driver
% specifications.)

% G. C. McBane  19 May 2007

\documentclass[12 pt,landscape]{article}
\usepackage{palatino}
\usepackage[dvips]{geometry}
\usepackage{gcard}
 \usepackage{fontenc}
 \usepackage{textcomp}

\usepackage{shapepar}
\usepackage{xcolor}

\usepackage{frcursive}
\usepackage[T1]{fontenc}
%\newcommand{\setfont}[2]{{\fontfamily{#1}\selectfont #2}}
\newenvironment{myfont}{\fontfamily{frc}\selectfont}{\par}

% user should set next four lengths to taste; defined for a single panel
% after folding.  All four panels use the same margins.
% Here, edge and gutter are set the same, as are top and bottom; that's
% not required, and it's okay to use 4 different values.
\setlength{\gcguttermargin}{8 mm} % inside edge of textblock  
\setlength{\gcedgemargin}{\gcguttermargin}  % outside edge
\setlength{\gctopmargin}{6 mm}        % top
\setlength{\gcbottommargin}{\gctopmargin}  % bottom


\begin{document}

\begin{frontcover}
\centering 
\huge
\textit{To Flavia\ldots}
\end{frontcover}


% back cover; pushed down to 0.5 cm above bottom margin
\begin{backcover}
\centering
\small
%THIS SPACE INTENTIONALLY LEFT BLANK
\textcolor{red}{\heartpar{Tieni ben stretto tutto il tuo tempo. Dipenderai meno dal domani, se saprai dominare l'oggi. Mentre la si differisce, la vita trascorre. Tutto è altrui, solo il tempo è nostro. La natura ci ha affidato il possesso di quest'unico bene, fugace e inafferrabile, da cui ci può espellere chiunque. Tanta è la loro stoltezza che mentre gli uomini accettano di essere responsabili di cose loro affidate, siano pure vilissime e sicuramente sostituibili con altre, nessuno si ritiene debitore per aver ricevuto del tempo, mentre è l'unica cosa che non si può restituire, per quanto riconoscenti. (Seneca)}}
\end{backcover}
                                
% inside left
\begin{insideleft}
\centering
\small
%THIS SPACE INTENTIONALLY LEFT BLANK
\textcolor{red}{\heartpar{Your children are not your children. 
They are the sons and daughters of Life's longing for itself. 
They come through you but not from you, 
And though they are with you, yet they belong not to you. 
You may give them your love but not your thoughts. 
For they have their own thoughts. 
You may house their bodies but not their souls, 
For their souls dwell in the house of tomorrow, which you cannot visit, not even in your dreams. 
You may strive to be like them, but seek not to make them like you. 
For life goes not backward nor tarries with yesterday. 
You are the bows from which your children as living arrows are sent forth... (Kahlil Gibran)}}
\end{insideleft}

% inside right
\begin{insideright}
 \begin{center} % same effect as \centering used for front cover
\Huge
\textit{On your last day\\
of high school}
 \end{center}
\end{insideright}

\end{document}
