\documentclass[10pt]{meetingmins}
\setcommittee{Student Affairs Committee}
\setmembers{
	\chair{Donatella Delfino},
	Lynne Davidson,
	Mechthild Schmidt,
	Steve Valenti,
	Reed Hodkin,
	Chris Piegaro (ex officio),
	Teresa Gargiulo (ex officio)
}
\setdate{February 12, 2016}
\setpresent{
\chair{Donatella Delfino},
Lynne Davidson,
Mechthild Schmidt,
Steve Valenti,
Reed Hodkin,
Chris Piegaro (ex officio)
}
\absent{Teresa Gargiulo (CCTOP meeting)}
%\alsopresent{B.~There}
\begin{document}
\maketitle
\section{Announcement}
The Committee agreed to pursue the following projects:
\begin{hiddenitems}
\item McGhee Community Building Event;
\item Enhanced engagement in online pedagogy;
\item Review of the five questions in the University-wide survey that McGhee can customize (see minutes of the 10/29/15 meeting.)
\end{hiddenitems}	
	
%%%%%%%%%%\section{Announcements}
%%%%%%%%%%\begin{hiddenitems}
%%%%%%%%%%\item
%%%%%%%%%%The dean is coming today.
%%%%%%%%%%\item
%%%%%%%%%%The dean has canceled.
%%%%%%%%%%\end{hiddenitems}
\section{McGhee Community Building Event}
\subsection{Objective}
An opportunity  to share information and feedback about McGhee club organization and events. Since McGhee students have unique needs, we will look for feedback on what we are missing and what types of additional programming students desire.
\subsection{Audience}
McGhee club officers and faculty advisors. The meeting will be open to all interested McGhee faculty, students and academic advisors.
\subsection{Structure} 
An afternoon or evening meeting (possibly on a Friday) in the 5th floor student lounge at 7 E 12th St. Participants will also have the opportunity to attend virtually. We envision the meeting to be a town hall. At the end of the meeting, participants will fill out a survey form to  give individual feedback on their experience with and level of satisfaction with club events, as well as suggestions on how to enhance the club experience.
\subsection{Organizers}
The McGhee Student Association, of which Reed Hodkin is an officer, will organize the event. The McGhee Student Association will consult with the SPS Office of Student Life, the SPS Undergraduate Student Council and the McGhee Student Affairs Committee.
\subsubsection{Timeline}
The event will take place in late March or early April.
\begin{hiddensubitems}
\item
Decide on a date, depending on the availability of the 5th floor lounge.
\item
Discuss and work with the Office of Student Life  and the Undergraduate Student Council.
\item Prepare promotional materials. 
\begin{hiddensubitems}
\item Flyers;
\item Social media (the SPS social media coordinator will be involved as well);
\item Ask faculty to advertise the event in class and through NYUClasses.
	
	\end{hiddensubitems}
	\item Promote the event.
\end{hiddensubitems}
\section{Enhanced engagement in online pedagogy}
\subsection{Objective}
Collect  best practices adopted by McGhee faculty to increase substantive and timely participation in online classes.
\subsection{Background}
In Fall 2015, the Committee discussed what constitutes participation in both onsite and online classes. The Committee agreed that timeliness and substantiveness of participation are key components of a successful student and faculty experience in an online classroom. The Committee shared the following best practices:
\begin{items}
	\item Small groups within the forums are a great way to boost team interactions and create rapport amongst students.
	\item Make posting in forums effective by, for example, requiring students to post feedback to a reading by day 3 of the week, and then posting substantive comments to other students' feedback by day 5 of the week.
	\end{items}
\subsection{Structure}
The Committee will distribute an online survey to McGhee faculty. The survey will ask faculty to share one strategy they use to increase student engagement when teaching online. The Committee will compile the results of the survey and share them with the McGhee faculty and administration.
\subsubsection{Timeline} The survey will be distributed in late March or early  April.
\subsubsection{For Further Discussion} \begin{subitems}
	\item Should we ask more than one question? 
\item The response rate may be low. 
\end{subitems}
\section{Old Business}
\begin{items}
	\item We will review the minutes of the Nov.~19 meeting at our next meeting. At the Nov.~19 meeting we brainstormed the idea of  organizing a town hall meeting for McGhee clubs.  
	\item We had an informal meeting on Dec.~11, where we did not take minutes. 
%	\priormins
\end{items}
%%%%%%%%%%\section{New Business}
%%%%%%%%%%\begin{items}
%%%%%%%%%%	\item
%%%%%%%%%%	We will teach classes next semester.
%%%%%%%%%%	\item
%%%%%%%%%%	We will do research next semester.
%%%%%%%%%%\end{items}
\vspace{1em}
\nextmeeting{We agreed to schedule the next meeting by email, using a survey form.}
\end{document}

