\documentclass[10pt]{meetingmins}
\setcommittee{Student Affairs Committee}
\setmembers{
	\chair{Donatella Delfino},
	Lynne Davidson,
	Mechthild Schmidt,
	Steve Valenti,
	Reed Hodkin,
	Chris Piegaro (ex officio),
	Teresa Gargiulo (ex officio)
}
\setdate{April 20, 2016}
\setpresent{
\chair{Donatella Delfino},
Reed Hodkin, Steve Valenti,
Chris Piegaro (ex officio),
Teresa Gargiulo (ex officio)
}
\absent{Lynne Davidson,
Mechthild Schmidt }
%\alsopresent{B.~There}
\begin{document}
\maketitle

\section{Needs-Assessment Survey Form}
\subsection{Launch and Timeline}
\begin{subitems}
	\item The survey has been launched today via an email to all McGhee students.
\item The survey will remain open until May 2nd.
	\item Since the survey is on Qualtrics, reports are available before May 2nd.
\end{subitems}
\subsection{Further Steps on Advertising the Survey} 
\begin{subsubitems}
	\item Reed will reach out to McGhee club officers and other McGhee students to encourage them to participate. 
	\item Teresa  will send  an email to all McGhee full time faculty with the link to the survey.
	\item The survey link will not be posted on Facebook, because we want to avoid the situation where non-McGhee students take the survey.
\end{subsubitems}

\subsection{Possible Action Items for 2016-2017} 
\begin{subsubitems}
 \item Develop guidelines for implementation of the results of the McGhee Needs-Assessment Survey.
\item Review the McGhee retention data provided by the Office of Institutional Research.
\item Collaborate with the McGhee Student Association to develop initiatives directed at improving the NYU experience of McGhee students.
\item Review the results of the NYU Student Experience survey. The results will be available in Fall 2016.
\end{subsubitems} 



\section{Accomplishments} The Committee had a very productive academic year, discussing a wide range of topics:
\begin{items}
	\item Attendance and participation policies;
	\item Course design to increase online participation, both in online and on-site classes;
\item Development and launch of the McGhee needs-assessment survey.
\end{items}
\section{Old Business}
\priormins

\vspace{1em}
\nextmeeting{Wednesday May 11, 2:30 pm to 4 pm (room 333).} Carmelita Blake and Harriet Oster, who will serve on the Committee next year, will be invited to attend.
\end{document}

