\documentclass[11pt,dvipsnames]{article}

\usepackage{etex}
\usepackage{amssymb,amsmath,multicol} %<-- InWorksheetExam1 i also have fancyhdr,

\usepackage[metapost]{mfpic}
\usepackage[pdftex]{graphicx}

\usepackage{pst-plot}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

\usepackage{tikz}
\usepackage{tkz-2d}
\usepackage{tkz-base}
\usetikzlibrary{calc}
\usepackage{color}
\usepackage[inline]{enumitem}
\usepackage{refcount}%<-- non in WorksheetExam1

\usepackage[linewidth=1pt]{mdframed}

\usepackage{caption}
%\renewcommand{\headrulewidth}{0pt}

%%These three lines are for the typewriter font. Comment them out if I don't want the font.
%%%%%%\renewcommand*\ttdefault{lcmtt}
%%%%%%\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
%%%%%%\usepackage[T1]{fontenc}
%%%%%%

\usepackage{tabularx, booktabs}

\opengraphsfile{Wk6_Questions_Spring_16}

\begin{document}
%\thispagestyle{empty}
\begin{enumerate}[label= {\bf  \arabic*:}]
	\item True or False?
	\begin{enumerate}
		\item $\displaystyle \frac{1}{x+y}=\frac{1}{x}+\frac{1}{y}$
		\item $\displaystyle \frac{y}{x+y}=\frac{1}{x}$
	\end{enumerate}
	\item  A car is driven 10,000 miles. Write a formula for the gas consumption $y$ (in gallons) if the car gets $x$ miles per gallon (mpg).
\item \label{item:bah}Many people are concerned with improving gas mileage of cars to reduce the impact of
greenhouse gases on the environment. Assume that a person drives 10,000 miles per year and is
contemplating changing from a current vehicle to a new one.
Rank order the following changes in vehicles in terms of their benefit to the environment (i.e.,
which new car would reduce gas consumption the most compared to the amount used by the
original car). Use the ranks 1, 2, 3, 4, and 5. Use 1 for the change that would reduce gas
consumption the most compared to the original car, and 5 for the change that would reduce gas
consumption the least compared to the original car. 


\begin{tabular}{|l|l|l|}
\hline
Original car & New car & Rank \\ \hline
16 mpg & 20 mpg &  \\ \hline
22 mpg & 24 mpg &  \\ \hline
18 mpg & 28 mpg &  \\ \hline
34 mpg & 50 mpg &  \\ \hline
42 mpg & 48 mpg &  \\ \hline
\end{tabular}

Note: Question~\ref{item:bah} was created by two professors at the Fuqua School of Business at Duke University, Richard Larrick and Jack Soll, as an example for a paper they published in {\emph{Science}} in 2008.
\item  You are offered two different deals on a product: the first deal offers you a 33\% discount on the price $P$ of a product, while the second deal offers you 33\% more product  for the price $P$. Which of the two options is the best deal, and why? Or are the two options equivalent?
\item An alcohol solution consists of 10 gallons of water and $x$ gallons of alcohol. Let $f(x)$ be the ration of the volume of alcohol to the total volume of liquid.
\begin{enumerate}
	\item Find a formula for $f(x)$.
	\item  Evaluate $f(1)$ and explain what it means in the context of this problem.
	\item What is the $x$ intercept of $f(x)$? What does it mean in the context of this problem?
	\item As $x$ becomes larger and larger, what happens to the outputs of $f(x)$? For example, do they become larger and larger ($f(x)\to \infty$)? Do they get closer and closer to a fixed number? What does your answer mean in the context of this problem?
	
\end{enumerate}
\item For each of the functions listed below, find the domain, the $y$-intercept, and the $x$-intercept(s). 
\begin{enumerate}
	\item $\displaystyle f(x)=\frac{1}{x-1}$. (Note: this is a transformation of $\displaystyle y=\frac{1}{x}$) As $x\to \infty, f(x)\to \ldots$
	\item $\displaystyle g(x)=\frac{x-2}{x^2-1}$.  Find $g(1.1), g(1.01), g(1.001), g(1.0001)$. What happens to the $y$ values of this function as I replace $x$ with numbers bigger than 1 and getting closer and closer to 1?
	\item $\displaystyle g(x)=\frac{x-2}{x^2+1}$.
	
\end{enumerate}
\end{enumerate}

\end{document}                 