\documentclass[11pt,dvipsnames]{article}

\usepackage{etex}
\usepackage{amssymb,amsmath,multicol} %<-- InWorksheetExam1 i also have fancyhdr,

\usepackage[metapost]{mfpic}
\usepackage[pdftex]{graphicx}

\usepackage{pst-plot}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

\usepackage{tikz}
\usepackage{tkz-2d}
\usepackage{tkz-base}
\usetikzlibrary{calc}
\usepackage{color}
\usepackage[inline]{enumitem}
\usepackage{refcount}%<-- non in WorksheetExam1

\usepackage[linewidth=1pt]{mdframed}

\usepackage{caption}
%\renewcommand{\headrulewidth}{0pt}

%%These three lines are for the typewriter font. Comment them out if I don't want the font.
%%%%%%\renewcommand*\ttdefault{lcmtt}
%%%%%%\renewcommand*\familydefault{\ttdefault} %% Only if the base font of the document is to be typewriter style
%%%%%%\usepackage[T1]{fontenc}
%%%%%%
\makeatletter
\newcommand{\inlineitem}[1][]{%
	\ifnum\enit@type=\tw@
	{\descriptionlabel{#1}}
	\hspace{\labelsep}%
	\else
	\ifnum\enit@type=\z@
	\refstepcounter{\@listctr}\fi
	\quad\@itemlabel\hspace{\labelsep}%
	\fi}
\makeatother
\parindent=0pt

\usepackage{tabularx, booktabs}


\opengraphsfile{Wk8_Questions_Spring_16}

\begin{document}
%\thispagestyle{empty}
The difference between linear growth and exponential growth is that with linear growth, a quantity increases or decreases by a constant number, while in exponential growth, a quantity increases or decreases by a constant percent.

Exponential growth leads to repeated doubling, and exponential decay leads to repeated halving. The time it takes for a population to double (assuming that it is growing exponentially) is called the doubling time. The time it takes for a quantity to become half of what it was initially (assuming it decreases exponentially) is called the half life.


	\begin{enumerate}[label= {\bf  \arabic*:}, leftmargin=*]
		\item A new car was sold at \$30,000. Assume that the value of the car depreciates by 5\% per year. What is the value of the car one year after the purchase? Two years after the purchase? What is a formula that gives the value $V(t)$ of the car after $t$ years?
		
\item Suppose a single bacterium is placed in a bottle at 11:00 am. It grows and at 11:01 am it divides into two bacteria. The two bacteria grow and at 11:02 am each of them divides into two bacteria, and so on. The bacteria continues to double every minute, and the bottle is full at noon. %The bottle contains $\displaystyle 2^{60}$ bacteria, which are doomed, because the bottle is full. 
%Let's try to understand how the bacteria can avert disaster.

\begin{enumerate}
	\item Here are three possible options for the number of bacteria in the bottle at 11:30 am. Which is correct, and why?
	\begin{enumerate}[label= { \textcolor{blue}{(\Alph*)}}]
		\item $2\times 30$ \inlineitem $\displaystyle 2^{30}$ \inlineitem $\displaystyle 2\times 10^{30}$
	\end{enumerate}
	\item How many more bacteria are in the bottle at 11:31 am than at 11:30 am? How do you know?
\item  At what time is  the bottle half-full? 

\item  It is 11:56 am. What fraction of the bottle is full at this time?
 


%%%%%%\item  At 11:56 am, the bacteria in the first bottle distribute themselves equally into three additional empty bottles (so at 11:56 am there are four bottles, each containing the same number of bacteria). How many minutes will it take for the four bottles to be full? 

\item Assume that each bacterium has a volume of $\displaystyle 10^{-21} \text{m} ^3$. The volume of the Earth is $\displaystyle 1.083\times 10^{21 }\text{m}^3$. How long would it take until their volume exceeds the volume of the Earth?

%\item The total surface area of the Earth is about 
%$\displaystyle 5.1 \times 10^{14} \text{m} ^2$. After two hours of doubling, how thick would the layer of bacteria over the Earth be? Would it be knee-deep? (Note: A volume divided by an area gives a depth.)

\end{enumerate}


	\item A town's population increases in one year from 100,000 people to 100,100 people.
	\begin{enumerate}
		\item If the population grows linearly, what is the population size after 20 years?
		\item if the population grows exponentially, what is the population size after 20 years?
	\end{enumerate}
	\item A country experiences a period of hyperinflation, where the price of food increases by 25\% per month. If a family food bill for a given month was \$200, what is the food bill for the family 2 months later? (Assume that the family purchased the same items, and in the same quantity, in the two months under consideration.)

\item The population of an endangered species is decreasing by 10\% per year. How many years will it take the population to drop by half?
\item A population is growing by 10\% per year. By what factor will it grow in 10 years?
\item A population doubles every 4 hours. By what factor does it grow in 12 hours?
\end{enumerate}
\end{document}                 