\documentclass[11pt,dvipsnames]{article}

\usepackage{etex}
\usepackage{amssymb,amsmath,multicol} %<-- InWorksheetExam1 i also have fancyhdr,

\usepackage[metapost]{mfpic}
\usepackage[pdftex]{graphicx}

\usepackage{pst-plot}
\usepackage{pgfplots}
\pgfplotsset{compat=1.9}

\usepackage{tikz}
\usepackage{tkz-2d}
\usepackage{tkz-base}
\usetikzlibrary{calc}

\usepackage[inline]{enumitem}
\usepackage{refcount}%<-- non in WorksheetExam1

\usepackage{caption}
%\renewcommand{\headrulewidth}{0pt}

\newcommand{\vasymptote}[2][]{
    \draw [densely dashed,#1] ({rel axis cs:0,0} -| {axis cs:#2,0}) -- ({rel axis cs:0,1} -| {axis cs:#2,0});
}

\newcommand{\inlineitem}[1][]{%
\ifnum\enit@type=\tw@
    {\descriptionlabel{#1}}
  \hspace{\labelsep}%
\else
  \ifnum\enit@type=\z@
       \refstepcounter{\@listctr}\fi
    \quad\@itemlabel\hspace{\labelsep}%
\fi}

\usetikzlibrary{automata}

\usepackage{hyperref}% http://ctan.org/pkg/hyperref



\opengraphsfile{Wk_1_Questions_Spring_16}

\begin{document}
\thispagestyle{empty}
\begin{enumerate}[label=$\blacktriangleright$ {\bf  \arabic*:}]
\item How is the slope of a line related to the “inclination” of its graph?

\item If you have two data points, how do you find the equation of the line through the two points? Find the equation if the pair is $(2,0)$, $(3,1$).  Does the method you used to find the equation change, if the pair is $(2,0)$, $(3,0)$? How about the pair $(0,2)$ and $(0,3)$?

\item If I start with $y = mx + b$ and I change $b$ (but don’t change $m$), how does the new graph look like?

\item Can a line have a slope of zero?

\item What does it mean to solve a system of two equations in two unknowns?

\item How do you check if the point (1,2) verifies the inequality  $2x-4y<7$?



\item A furniture manufacturer makes wooden tables and chairs. The production process involves two basic types of labor: carpentry and finishing. A table requires 2 hours of carpentry and 1 hour of finishing, and a chair requires 3 hours of carpentry and $\displaystyle \frac{1}{2}$ hour of finishing.  The manufacturer's employees can supply a maximum of 108 hours of carpentry work and 20 hours of finishing work per day. 
\begin{enumerate}[label=$\diamondsuit$ {\bf  \arabic*:}]
\item Call $x$ the number of tables built in one day, and $y$ the number of chairs built in one day. Write an inequality (involving $x$ and $y$) describing the fact that the employees can provide at most 108 hours of carpentry work to build $x$ tables and $y$ chairs in a day.
\item  Write another inequality (involving $x$ and $y$) describing the fact that the employees can provide at most 20 hours of finishing work to build $x$ tables and $y$ chairs in a day.
\item If the employees provide exactly 108 hours of carpentry work and exactly 20 hours of finishing work in one day, how many chairs and how many tables are built on that day?
\end{enumerate}
\end{enumerate}
\end{document} 
              